Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-24 WRITEUP/ms.tex
MIPS 24 micron

The emission in the IRAC images is slightly extended. We thus use the
{\it HST} image ($\sim$0\farcs07 resolution) to determine
origins of their centroids, all of which are found to be
centered at the position corresponding to the lensed emission from the
background galaxy. To recover the diffuse background emission, we subtract a
point source model centered on the lensing galaxy, using the average
FWHM found by fitting a Gaussian profile to several field stars
with the \ncode{imexam} routine of IRAF.
We perform aperture photometry on the residual image
to obtain decomposed flux measurements from the background galaxy.
The photometries for the foreground galaxy are then obtained
by subtracting the fluxes decomposed for the background source
from the observed total flux. The resulting photometry in
\Tab{photometry} are obtained after performing aperture correction
described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
correct for the fact that the imaging was calibrated
using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
perform aperture photometry. This step was taken to provide
constraints on the Wien tail beyond the dust peak of the
spectral energy distribution (SED) of RXJ1131.
Details of the SED modeling is presented in \Sec{SED}.

@@

% Check with Shane
{\bf NEEDS EDIT}
Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
posterior probability distribution function (PDF).
In each model, we require a target acceptance rate of $\sim$0.25$-$0.5
and check for chain convergence by inspecting the trace plots
AND BLAH to verify we are sampling beyond an autocorrelation time.
We employ $\sim$50,000 samples as the initial ``burn-in'' stage
to stabilize the Markov chains (which we then discard) and
use the final $\sim$5,000 steps, sampled by 128 walkers, to identify
the posterior. Here, we
identify the best-fit model and the quoted uncertainties using the
median and the 68\% confidence intervals in the marginal PDFs.
\input{table_medianLens}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.455\textwidth]{../Figures/bestfit_PV.eps}
\caption{PV slice along the major axis in the source plane at PA\,=\,121\degr.
Dashed line shows the best-fit rotation curve using an arctangent model.
The vertical error bars show the channel width for
each model and the horizontal error bars are the
1$\sigma$ uncertainties on the source plane positions.
DR may suggest include MC simulation fits, maybe I will do that later.
 \label{fig:PV}}
\end{figure}

@@

\subsection{SED modeling} \label{sec:SED}
By fitting a power-law spectrum $S_\nu \propto \nu^\alpha$ to the decomposed
IRAC photometry. We find a spectral index of $\alpha\sim-$1.9 and
$\alpha\sim-$0.85 for the lensing galaxy and RXJ1131, respectively.
This is consistent with the mean spectral slope of optical quasars
($\alpha\sim-$1, Elvis et al. 1994; Neugebauer et al. 1979).
For comparison, broad-line AGN from the AGN and Galaxy
Evolution Survey (AGES, C. S. Kochanek et al., in prep) have 3.6$-$8
\micron slopes of $\alpha$ = $-$1.07$\pm$0.53 (Stern et al. 2005).

We extrapolated a power-law to 24 \micron to decompose the flux
at 24 \micron in MIPS.
Since the contribution from AGN is not taken into account in SBURT, it is expected that the SEDs of AGN candidates show an excess in the MIR, owing to hot dust around the central massive black hole,
NIR not corrected for extinction.

% describe the SED model
We fit SED models to the photometry from BLAH$-$BLAH \micron
using a modified-blackbody function
with a power-law attached to the blue side.
% We added blah\% calibration uncertainties on the PdBI data.
We include
the IRAS 60\micron and 100\micron upper limits
to constrain the dust peak. We also fit SED models
including the decomposed 24.0\micron data.
identical to the modified blackbody fit,
where the Wien side is removed and replaced by MIR power-law consistent with any mid-IR data available.
We find a power-law slope of BLAH,
Previous studies find that in the absence of mid-IR data, a powerlaw slope of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).

% describe mbb_emcee
We check convergence of our chains by requiring that the autocorrelation length for each model parameter is
several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
The code treats the instrument response.
flux using the set of photometric filters used to obtain the observations.
% parameter estimation problem
For these parameter estimation problems using MCMC to sample,
the full answer is the full joint posterior PDF.
We here report the summary statistics (global mode (where min. chi),
marginal mode (in log file),
posterior median (instead of posterior means; need to compute) and the
1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.

% upper limit using decomposed 24 um
% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
The best-fit SEDs are shown in \Fig{SED} and the resulting parameters
are listed in \Tab{SED}.
Our SED model find a rest-frame characteristic dust temperature of BLAH
(cf. 60$-$70\,K in the cores of local ULIRGs/SB; Pauzzo+11, Rangwala+10),
\fir (rest-frame 42.5-122.5 \micron) of blah, and a dust mass of blah.
For the mass absorption coefficient, we adopt BLAH (rest frame; Dunne et al. 2003).

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}
\caption{
WISE flux is higher than the IRAC data, probably just due to smaller aperture used in IRAC.
Spitzer IRAC: Aperture flux in 5\farcs diameter with aperture correction applied.
Spitzer/MIPS: PSF fit flux, as source size <
native PSF FWHM of 6".
Might want to add NVSS constraints.
The data are not corrected for dust extinction.
 \label{fig:SED}}
\end{figure*}

\subsubsection{SB versus AGN contribution}
To derive the intrinsic properties, we correct for lensing using the
median magnification factor derived from the CO lens models.
Assuming a Salpeter initial mass function, we find the SFR of blah using the
lensing-corrected \fir luminosity.

>>>>

The emission in the IRAC images is slightly extended. We thus use the
{\it HST} image ($\sim$0\farcs07 resolution) to determine
origins of their centroids, all of which are found to be
centered at the position corresponding to the lensed emission from the
background galaxy. To recover the diffuse background emission, we subtract a
point source model centered on the lensing galaxy, using the average
FWHM found by fitting a Gaussian profile to several field stars
with the \ncode{imexam} routine of IRAF.
We perform aperture photometry on the residual image
to obtain decomposed flux measurements from the background galaxy.
The photometries for the foreground galaxy are then obtained
by subtracting the background emission from the
observed total flux. The resulting photometry in
\Tab{photometry} are obtained after performing aperture correction
described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
correct for the fact that the imaging was calibrated
using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
perform aperture photometry.
We then fit a power-law spectrum $S_\nu \propto \nu^\alpha$ to the
decomposed IRAC photometry to disentangle the observed total flux
at MIPS 24\micron. We find a spectral index of $\alpha\sim-$1.8 and
$\alpha\sim-$0.85 for the lensing galaxy and RXJ1131, respectively.
This is consistent with the mean 3.6$-$8\micron spectral slope of
$\alpha$\,=\,$-$1.07$\pm$0.53 found for unobscured AGN
\citep{Stern05a}. An extrapolation of the fit to 24\micron
yields 33.96$\pm$0.01\,mJy and 25.19\,$\pm$\,0.03\,mJy
for the foreground galaxy and RXJ1131, respectively.
We note that the IRAC photometry includes
contributions from old stellar population and is prone to
dust extinction. Hence, the decomposed fluxes are only
our best estimate of the warm dust emission.
We incorporate the decomposed 24\micron point in our
SED fitting to provide some constraints on
the Wien tail beyond the dust peak
of the spectral energy distribution (SED) of RXJ1131.
Details of the SED modeling is presented in \Sec{SED}.

@@

Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
posterior probability distribution function (PDF).
In each model, we require a target acceptance rate of $\sim$0.25$-$0.5
and check for chain convergence by inspecting trace plots
and requiring the samples are beyond at least an autocorrelation time.
We thus employ $\sim$50,000 samples as the initial ``burn-in'' phase
to stabilize the Markov chains (which we then discard) and
use the final $\sim$5,000 steps, sampled by 128 walkers, to identify
the posterior. Here, we
identify the best-fit model and the quoted uncertainties using the
median and the 68\% confidence intervals in the marginal PDFs.
\input{table_medianLens}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.455\textwidth]{../Figures/bestfit_PV.eps}
\caption{PV slice along the major axis in the source plane at PA\,=\,121\degr.
Dashed line shows the best-fit rotation curve using an arctangent model.
The vertical error bars show the channel width for
each model and the horizontal error bars are the
1$\sigma$ uncertainties on the source plane positions.
DR may suggest include 68\& fits from MC simulation, maybe I will do that later.
 \label{fig:PV}}
\end{figure}

@@

\subsection{SED modeling} \label{sec:SED}
We fit dust SED models to the
24\micron$-$2.2\,mm photometry in \Tab{photometry}, where we also
include the IRAS 60\micron and 100\micron upper limits
to constrain the dust peak.
The fit is performed with the code
\ncode{mbb\_emcee} \citep[\eg][]{Dowell14a}, which
uses instrumental response curves to perform color correction on-the-fly.
The first SED model is a modified-blackbody
function with a power-law attached to the
blue/Wien side to account for an excess in the MIR owing to warm dust emission.
%We add $\sim$15\% calibration uncertainties in quadrature to obtain the total
%uncertainties for the PdBI continuum in our fitting procedure.

We find a power-law slope of BLAH,

% describe mbb_emcee
We check for chain convergence by requiring the autocorrelation
length for each model parameter is less than the number of steps
taken during the burn-in phase (which are then discarded).
% parameter estimation problem
For these parameter estimation problems using MCMC to sample,
the full answer is the full joint posterior PDF.
We here report the summary statistics (global mode (where min. chi),
marginal mode (in log file),
posterior median (instead of posterior means; need to compute) and the
1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.

% upper limit using decomposed 24 um
% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
The best-fit SEDs are shown in \Fig{SED} and the resulting parameters
are listed in \Tab{SED}.
Our SED model find a rest-frame characteristic dust temperature of BLAH
(cf. 60$-$70\,K in the cores of local ULIRGs/SB; Pauzzo+11, Rangwala+10),
\fir (rest-frame 42.5-122.5 \micron) of blah, and a dust mass of blah.
For the mass absorption coefficient, we adopt BLAH (rest frame; Dunne et al. 2003).
Previous studies find that in the absence of mid-IR data, a powerlaw slope of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).

We also fit an SED model excluding the decomposed 24.0\micron data.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}
\caption{
WISE flux is slightly higher than the IRAC point, probably due to a smaller
aperture used in IRAC extraction, both of which were taken from the archive.
Spitzer IRAC:
Aperture flux in 5\farcs diameter with aperture correction applied.
Spitzer/MIPS: PSF fit flux, as source size <
native PSF FWHM of 6".
Might want to add NVSS constraints.
The data are not corrected for dust extinction.
\label{fig:SED}}
\end{figure*}

\subsubsection{SB versus AGN contribution}
% brief argument
What does it imply to the dust properties if we see the QSO.. contribution to the hot dust is not as much as if we were viewing it edge-on? --> warm dust and cold dust.

We quantify the AGN contribution to total IR.
important how the power source differ from high-z or local.

To derive the intrinsic properties, we correct for lensing using the
median magnification factor derived from the CO lens models.
Assuming a Salpeter initial mass function, we find the SFR of blah using the
lensing-corrected \fir luminosity.
